Study of Higgs plus single top production using events with a same sign dimuon at the Large Hadron Collider

### 2019-11-22 tesis_hiram/Abstract/abstract.tex
n

% ************************** Thesis Abstract *****************************
% Use `abstract' as an option in the document class to print only the titlepage and the abstract.
%\begin{center}
%	\justifying
I present a study on the production of a Higgs boson plus a single top quark ($tH$) in same sign dimuon channel $\mu^\pm \mu^\pm$ using data published by the CMS experiment at CERN. By studying this
process I explore a Higgs production mechanism which has not yet been observed
experimentally. The expected sensitivity is estimated by using an Asimov dataset for 35.9 fb$^{-1}$ of proton-proton collisions and is extrapolated to the  high luminosity phase of the LHC (HL-LHC).
The sensivity is also studied for the model with inverted Yukawa coupling $k_t$=-1, where $k_t$ is the top-Higgs coupling parameter modifier, for comparison with the Standard Model.
%\end{center}

>>>>

% ************************** Thesis Abstract *****************************
% Use `abstract' as an option in the document class to print only the titlepage and the abstract.
%\begin{center}
%	\justifying
We present a study on the production of a Higgs boson plus a single top quark ($tH$) in same sign dimuon channel $\mu^\pm \mu^\pm$ using data published by the CMS experiment at CERN. By studying this
process, we explore a Higgs production mechanism which has not yet been observed
experimentally. The expected sensitivity is estimated by using an Asimov dataset for 35.9 fb$^{-1}$ of proton-proton collisions and is extrapolated to the high luminosity phase of the LHC (HL-LHC).
The sensitivity is also studied for the model with inverted Yukawa coupling $k_t$=-1, where $k_t$ is the top-Higgs coupling parameter modifier, for comparison with the Standard Model.
%\end{center}

### 2019-11-22 tesis_hiram/Abstract/resumen.tex
n

%\renewcommand{\absnamepos}{empty} % originally center
%\begin{center}
%	\justifying
Presento un estudio sobre la producci\'on del boson de Higgs y un top quark ($tH$) en el canal de 2 muones con el mismo signo $\mu^\pm \mu^\pm$ usando datos publicados por el experimento CMS en el CERN.
Estudiando este proceso se explora este mecanismo de producci\'on del boson de Higgs que a\'un no se ha detectado experimentalmente.
La sensibilidad esperada es calculada usando  datos de tipo Asimov para 35.9 fb$^{-1}$ de colisiones de prot\'on-prot\'on y es extrapolada la fase de alta luminosidad del LHC (HL-LHC).
La sensibilidad de la se\~nal es tambi\'en estudiada para el modelo con acoplamiento de Yukawa invertido $k_t$=-1, donde $k_t$ es el modificador del par\'ametro de acoplamiento de top-Higgs, en comparaci\'on con el Modelo Est\'andar.
%\end{center}

>>>>

%\renewcommand{\absnamepos}{empty} % originally center
%\begin{center}
%	\justifying
Se presenta un estudio sobre la producci\'on del boson de Higgs y un top quark ($tH$) en el canal de 2 muones con el mismo signo $\mu^\pm \mu^\pm$ usando datos publicados por el experimento CMS en el CERN.
Estudiando este proceso se explora este mecanismo de producci\'on del boson de Higgs que a\'un no se ha detectado experimentalmente.
La sensibilidad esperada es calculada usando  datos de tipo Asimov para 35.9 fb$^{-1}$ de colisiones de prot\'on-prot\'on y es extrapolada la fase de alta luminosidad del LHC (HL-LHC).
La sensibilidad de la se\~nal es tambi\'en estudiada para el modelo con acoplamiento de Yukawa invertido $k_t$=-1, donde $k_t$ es el modificador del par\'ametro de acoplamiento de top-Higgs, en comparaci\'on con el Modelo Est\'andar.
%\end{center}

### 2019-11-22 tesis_hiram/Acknowledgement/acknowledgement.tex
algo
fixes
n

And I would like to acknowledge Dr. Jos\'e Feliciano Ben\'itez Rubio for his contributions and advices in order to develop  and write this thesis. Also thank Dr. Dr. Javier Murillo and  Dr. Cristina Oropeza for their observations and advices in my formation. 
DR. Susana Alv\'arez for support

>>>>

And I would like to acknowledge Dr. Jos\'e Feliciano Ben\'itez Rubio for his contributions and advises in order to develop  and write this thesis. Also thank Dr. Javier Murillo and  Dr. Cristina Oropeza for their observations and advises in my formation. 
Dr. Susana Alv\'arez for support during the process of the thesis. Acknowledgments to CONACYT for supporting this thesis with financial aid.

### 2019-11-22 tesis_hiram/Chapter1/chapter1.tex
n

\section{General objetive and motivations}

Particle physics is a field of study of physics that studies the particles that create matter and its interactions to very small scale, even smaller than atoms. The particles analyzed in particle physics are the fundamental particles that compose the matter and the responsible for all forces of nature. All those particles and their properties are grouped in a theory called the Standard Model. Standard Model (SM) is a theory that describes the fundamental forces (except gravity) and classify the elementary particles in bosons (entire spin) and fermions (half spin).
The SM, created almost 50 years ago, has been the most successful theory in explain the phenomena in the subatomic world.

One of the particles of the SM, the Higgs Boson, was recently discovered in 2012 in the ATLAS and CMS experiments at CERN. The discovery of Higgs boson in proton proton collisions marked a new era in the particle physics due to its characteristic of giving the matter the property of mass, according to previous theories and predictions. Since then, people around the world are working in the Large Hadron Collider at CERN in order to detect the Higgs bosons in higher energies and different Higgs production processes. 
Also the impact of Higgs is also important in cosmology, where theoretical investigations relate the Higgs boson and the cosmic inflation.

In the recent years, there have been many studies in the Higgs production processes at CERN in pp collisions, such as gluon fusion (ggF), VBF, WH, ZH and $t\bar{t}$H and people have obtained consistent results in the search of Higgs in those processes. 
In this work, we will analyze the production of Higgs boson in association with a
single top quark (tH) in proton-proton collisions with the CMS experiment of the LHC.

The motivation of the work is this mechanism of production of the Higgs boson has not been observed before by any experiment. The exploration of Higgs production on the tH channel is subject relatively new. %The SM is used to study the tH channel and compare it with other Higgs production mechanisms results.
Many channels are yet out of
reach experimentally. At the same time, many theoretical
proposals are yet to be put on test. It is possible that studies on the Higgs boson give evidence of small deviations from the SM and test new physics that are beyond SM such as String Theory and Super-symmetry.

@@

\begin{center}
  \begin{figure}[ht]
    \centering
    \includegraphics[scale=0.3]{Chapter1/sm1.png}
    \caption{Standard Model to date \protect \footnotemark}
    \label{sm1}
  \end{figure}
\end{center}
 \footnotetext{Taken from \url{https://upload.wikimedia.org/wikipedia/commons/0/00/Standard_Model_of_Elementary_Particles.svg}
} 
The last group of the family are the bosons, which have a spin 1 and 0. 
There are 5 bosons: $W^{\pm}$, $Z$ with neutral charge are responsible for weak force; photon, a massless particle, is responsible for electromagnetic force; gluon which also massless, is related to strong force and Higgs boson, recently discovered, is in charge of give the property of mass to particles via Higgs mechanism. Bosons let other particles to interact, even themselves, which is shown in the figure \ref{sm}. 
The $W$,$Z$ and Higgs bosons, can interact with the most of the particles, while the gluon can only interact with quarks and itself.
Those bosons act as mediators in decays and creation of complex
particles, as mesons and baryons.
%In case of gravity, exist a theoretical particle, called graviton, that is the fundamental particle associated with the gravitational force. In case of its existance, it should have a spin 2 and mass 0.

@@

\begin{figure}
\centering
\includegraphics[width=12cm,height=7cm]{Chapter1/7-14xsec.eps}
\caption{
Cross section for different processes generated in a pp collision \protect \footnotemark }
 \label{csp}
\end{figure}

>>>>

\section{General objective and motivations}

Particle physics is a field of physics that studies the particles that create matter and their interactions to very small scale, even smaller than atoms. The particles analyzed in particle physics are the fundamental particles that compose matter and the responsible for all forces of nature. All those particles and their properties are grouped in a theory called the Standard Model (SM). SM is a theory that describes the fundamental forces (except gravity) and classifies the elementary particles in bosons (integer spin) and fermions (half spin).
The SM, created almost 50 years ago, has been the most successful theory in explaining the phenomena in the subatomic world.

One of the particles of the SM, the Higgs Boson, was recently discovered in 2012 in the ATLAS and CMS experiments at CERN. The discovery of Higgs boson in proton proton (pp) collisions marked a new era in particle physics due to its characteristic of giving matter the property of mass, according to previous theories and predictions. Since then, people around the world are working in the Large Hadron Collider (LHC) at CERN in order to detect the Higgs bosons in higher energies and different Higgs production processes. 
Also the impact of Higgs boson is also important in cosmology, where theoretical investigations relate the Higgs boson to the cosmic inflation.

In the recent years, there have been many studies in the Higgs boson production processes at CERN in pp collisions, such as gluon fusion (ggF), VBF, WH, ZH and $t\bar{t}$H and people have obtained consistent results in the search of the Higgs boson in those processes. 
In this work, we will analyze the production of a Higgs boson in association with a
single top quark (tH) in proton-proton collisions with the CMS experiment of the LHC.

The motivation of the work is that this production mechanism of the Higgs boson has not been observed before by any experiment. The exploration of Higgs production on the tH channel is a relatively new subject. %The SM is used to study the tH channel and compare it with other Higgs production mechanisms results.
Many channels are yet out of
reach experimentally. At the same time, many theoretical
proposals are yet to be put to test. It is possible that studies on the Higgs boson give evidence of small deviations from the SM and test new physics that are beyond SM such as String Theory and Super-symmetry.

@@

\begin{center}
  \begin{figure}[ht]
    \centering
    \includegraphics[scale=0.3]{Chapter1/sm1.png}
    \caption[Standard Model to date]{Standard Model to date \protect \footnotemark}
    \label{sm1}
  \end{figure}
\end{center}
 \footnotetext{Taken from \url{https://upload.wikimedia.org/wikipedia/commons/0/00/Standard_Model_of_Elementary_Particles.svg}
} 
The last group of the family are the bosons, which have a spin 1 and 0. 
There are 5 bosons: $W^{\pm}$, $Z$ with neutral charge are responsible for weak force; photon, a massless particle, is responsible for electromagnetic force; gluon which also massless, is related to strong force and Higgs boson, recently discovered, is in charge of give the property of mass to particles via Higgs mechanism. Bosons let other particles to interact, even themselves, which is shown in the figure \ref{sm}. 
The $W$,$Z$ and Higgs bosons, can interact with the most of the particles, while the gluon can only interact with quarks and itself.
Those bosons act as mediators in decays and creation of complex
particles, as mesons and baryons.
%In case of gravity, exist a theoretical particle, called graviton, that is the fundamental particle associated with the gravitational force. In case of its existance, it should have a spin 2 and mass 0.

@@

\begin{figure}
\centering
\includegraphics[width=12cm,height=7cm]{Chapter1/7-14xsec.eps}
\caption[Cross section for different processes generated in a pp collision]{
Cross section for different processes generated in a pp collision \protect \footnotemark }
 \label{csp}
\end{figure}
